%! TEX root = main.tex
% What we accomplished
\subsection{Reflection on research question}
In our research question we set out to investigate whether it was possible,
without deep financial knowledge, to utilize flash loans for monetary gain. We
have during the month of August tried to find an answer to this. While we have
not shown that it is possible, we have come up with the theory for doing so. So
in essence the answer probably lies in between yes and no. We would need to
spend some time doing more research, but it is not out of reach for the average
student at the science faculty to find arbitrage opportunities on the DeFi
market.

% We would like to continue
% - HOW FAST DO YOU NEED TO BE
% - Risk analysis
% - Gas prices
\subsection{Minimum required future work}
\noindent We also wanted to find out if it was possible to automate acting on
arbitrage opportunities. While we firmly believe this is possible, it does take
a great deal of effort to be able to do without some risk. Some of the things
we would need to continue working on is:

\paragraph{How important is it to utilize an arbitrage opportunity in the next
block?} When is the opportunity gone, and how many times will someone use it
before you. If the opportunity changes so much between detecting it, and
executing on it, that it is no longer profitable, we would still need to pay for
the gas used. If this happens a lot, we might end up with an overall
unprofitable system, even if some transactions makes money.
\paragraph{Gas prices} How much does it cost to run the code for an arbitrage
opportunity? Where is the cutoff, when it is no longer profitable due to the
cost of gas?
\paragraph{Fees incurred} Our theory assumes that there is no fees on the
exchanges, which there is. We would therefore need to adjust our calculations,
to take this into account. We do however believe, that this would be a
relatively minor adjustment to make.
\paragraph{Risk analysis} We would need to assess how much we can lose before it
becomes unprofitable, and what the actual profit is. If we e.g. will earn little
money, but risk to lose a lot, it would not be worth it in the end.\\\\
% We would rather have focused
% How it went
All in all the project went well and we managed to get the financial knowledge
on how to utilize arbitrage opportunities. Currently it is mostly the
implementation that is holding us back, from deploying the contract and earning
money. We spent more time on getting a broad knowledge. We could in hindsight
have limited our scope without losing the ability to find arbitrage
opportunities. The limited scope would be focused on understanding AMMs, and
arbitrage, and not have included the rest of the attacks/exploits that we have
discussed in this report.
